Appendix

### 2025-10-29 manuscript_rmarkdown/manuscript_appendix.tex
Fixed and updated text.

Table \ref{tab:comparison_methods_simulations_yeo_johnson_avg_residual}
shows the average normalised residual error for these transformation
methods. This metric is computed from the residual error and the
residual error of the central portion (\(\kappa = 0.70\)) for sequences
without and with outliers, respectively. In each experiment, the
respective residual error was normalised by dividing with the sequence
length, and can be interpreted as the average residual error of a single
sample. This reduces the effect of sequence length on the residual
error.

>>>>

Table \ref{tab:comparison_methods_simulations_yeo_johnson_avg_residual}
shows the average normalised residual error for these transformation
methods. This metric is computed from the residual error and the
residual error of the central portion (\(\kappa = 0.80\)) for sequences
without and with outliers, respectively. In each experiment, the
respective residual error was normalised by dividing with the sequence
length, and can be interpreted as the average residual error of a single
sample. This reduces the effect of sequence length on the residual
error.
